---
title: "Shiny App for Modeling Savings Ratio"
author: "Alex Cao"
date: "May 9, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny App

- This app models the Savings Ratio from the Disposable Income of Countries over the time period 1960-1970
- This data comes from the R dataset **LifeCycleSavings**
- The dependent variable is sr (savings ratio)
- The possible covariates are:
    i. dpi (per-capita disposable income)
    ii. ddpi (% growth rate of dpi)
    iii. pop15 (% of population under 15)
    iv. pop75 (% of population over 75)

## How-to-Use

- Select the points (countries) you want to model
- Select which covariates you want to include (two choices)

The App will automatically update the model after every step.  
__savings ratio ~ per-capita disposable income__ is the default model in the App.  
The __dpi__ covariate is included in every model (regardless of the check boxes)

## Model

```{r screenshot, fig.width=10, fig.height=6, fig.align='center'}
library(png)
library(grid)
img = readPNG('screenshot.png')
grid.raster(img)
```

## Full Linear Model

The linear model if you include all the countries and all the covariates available in the dataset is:

```{r model, comment=""}
data("LifeCycleSavings")
model = lm (sr ~ dpi + pop15 + pop75 + ddpi, data = LifeCycleSavings)
coef(model)
```
